---
title: "R + Git Practical (UI R Users Group, satRday)"
author: "Owokotomo Olajumoke Evangelina and Olusoji Oluwafemi Daniel"
date: "26/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Reading Data from GoogleSheets

To read the data from the participants googlesheet into **R**, you need the `googlesheets` and `googledrive` packages and perform some operations to save your token. Follow the steps below in an interactive **R** session.

1. If you don't have access to the spreadsheet yet, click on this [link](https://docs.google.com/spreadsheets/d/1o34C2x1V_BS6K4yiNXh60OzVRmzoEJNod64fd8X-gQA/edit?usp=sharing) to get access.

2. install the packages running 

```{r, eval=FALSE} 
install.packages(c("googledrive", "googlesheets")) 

```  

in **R**

3. Run the following to save your google drive token access.

```{r, eval=FALSE} 
library(googlesheets)
token <- gs_auth(cache = FALSE)
gd_token()
saveRDS(token, file = "my_sheet_token.rds")
```

The code block below will help you readin the data in the sheet into a **tibble** (sort of **dataframe** with some cool features) named *participant_data*. You will learn more about `tibbles` in the `tidyverse` part. 

```{r reading_data}
#install.packages(c("googledrive", "googlesheets"))
library(googlesheets)
library(googledrive)
library(stringr)

#path to my saved token. change this to path to your own saved token
token <- googledrive::drive_auth(oauth_token = "../../my_sheet_token.rds")

#get the name of a spreadsheets in your drive
sheet_names <- googledrive::drive_find(type = "spreadsheet")$name

# search for the sheet with the name Training Participants
participant_sheet <- sheet_names[str_detect(sheet_names, "Training Participants")]

#register the sheet
gs_participant <- googlesheets::gs_title(participant_sheet)

#finally read the data
participant_data <- gs_read(gs_participant, ws = "Form Responses 1")

```


Congratulations, you have successfully read in the data. Now, let's try to use that data for some reporting and graphs. Create a **R** code block to report the associated numbers to each section. You can as well report these numbers in graphs of your choice.

## Gender Distribution of Participants

The percentage of ladies in this tutorial is... I am guessing we need more `RLadies`.


## Operating System Mostly Used


Well quite a number of us should be using windows. Possibly some Mac but I will be surprised to see a linux based OS.

## R Experience


I think most of us will be somewhere in the middle. 

After you are done, save this file and push to the repo you created on **GitHub**.


